### 2021-03-29 Chapter-3/Chapter-3.tex
Updates from Overleaf

\section{Illustrative examples}

\section{Our Theoretical Frameworks}
We now discuss how to model observations ($O$), which are the direct information
that an adversary can get during the attack.

>>>>

\section{Examples}
\subsection{Secret-dependent Control-flow Transfers}

\subsection{Secret-dependent Data Accesses}

\section{Our Theoretical Frameworks}
\begin{figure}
    \centering
    \includegraphics[width=.35\columnwidth]{./figures/chapter3/attack.pdf}
    \caption{A side-channel attack}\label{fig:side-channel-attack}
\end{figure}

We now discuss how to model observations ($O$), which are the direct information
that an adversary can get during the attack.
